TacticToe: Learning to Prove with Tactics

### 2018-03-21 tactictoe_jv.tex
minor

The different components depicted in Fig~\ref{fig:components} give a 
high-level overview of the techniques necessary to generate 
tactic-level proofs by learning from recorded knowledge. From a formal library 
of ITP proofs, we extract and record tactic invocations 
in Section~\ref{sec:recording}. Based on such training examples, we
  build efficient machine learning classifiers in Section~\ref{s:prediction}.
  Modification of the knowledge base, shown as the training loop in 
  Fig~\ref{fig:components} and
  achieved by orthogonalization in Section~\ref{sec:ortho} and completed by 
  an abstraction technique in Section~\ref{sec:synthesis},
  improves the quality of the predictions.
  And the preselection method described in Section~\ref{sec:presel} increases 
  the speed of the prediction algorithm.
  The learned predictors relying on this knowledge guide the proof search 
  algorithm presented in Section~\ref{sec:proofsearch}.
  The search algorithm explores different proof paths in the proof tree which 
  is defined in Section~\ref{sec:prelim}. 
  The result, if
  successful, is a verified human-level proof composed of \holfour
  tactics minimized in Section~\ref{sec:proofdisplay}. And in 
  Section~\ref{s:experiments}, we evaluate the system 
  on a large set of theorems originating from \holfour.
  The generated proofs are compared with human proofs in 
  Section~\ref{sec:case_study}.

>>>>

The different components depicted in Figure~\ref{fig:components} give a 
high-level overview of the techniques necessary to generate 
tactic-level proofs by learning from recorded knowledge. From a formal library 
of ITP proofs, we extract and record tactic invocations 
in Section~\ref{sec:recording}. Based on such training examples, we
  build efficient machine learning classifiers in Section~\ref{s:prediction}.
  Modification of the knowledge base (shown as the training loop in 
  Figure~\ref{fig:components})
  achieved by orthogonalization in Section~\ref{sec:ortho} and completed by 
  an abstraction technique in Section~\ref{sec:synthesis}
  improves the quality of the predictions.
  And the preselection method described in Section~\ref{sec:presel} increases 
  the speed of the prediction algorithm.
  The learned predictors relying on this knowledge guide the proof search 
  algorithm presented in Section~\ref{sec:proofsearch}.
  The search algorithm explores different proof paths in the proof tree which 
  is defined in Section~\ref{sec:prelim}. 
  The result, if
  successful, is a verified human-level proof composed of \holfour
  tactics minimized in Section~\ref{sec:proofdisplay}. And in 
  Section~\ref{s:experiments}, we evaluate the system 
  on a large set of theorems originating from \holfour.
  The generated proofs are compared with human proofs in 
  Section~\ref{sec:case_study}.
